Paper

### 2025-03-14 paper/paper.qmd
variable renames

Using the posterior distributions as inputs to the simulation model, as described in @sec-model-calibration, the model was able to generate scenarios of outbreaks that closely matched the observed data (see @fig-posterior-predictive-check). In these simulated scenarios, the pre-outbreak baseline rate was a median of `r round(pre_outbreak_uniform_sims_rates$rate_mean, 2)` cases per 1000 patient days \[interquartile (IQR) range `r round(pre_outbreak_uniform_sims_rates$rate_q_low, 2)`--`r round(pre_outbreak_uniform_sims_rates$rate_q_high, 2)`\], compared with the real rate of 1.25 cases per 1000 \[IQR 0.94--1.56\]. During the outbreak period, simulations had a mean rate of `r round(outbreak_sims_rates$rate_mean, 2)` \[IQR `r round(outbreak_sims_rates$rate_q_low, 2)`--`r round(outbreak_sims_rates$rate_q_high, 2)`\] cases, compared with the real mean rate of 3.74 \[IQR 3.32--4.41\] (see @fig-simulated-rates).

>>>>

Using the posterior distributions as inputs to the simulation model, as described in @sec-model-calibration, the model was able to generate scenarios of outbreaks that closely matched the observed data (see @fig-posterior-predictive-check). In these simulated scenarios, the pre-outbreak baseline rate was a median of `r round(pre_outbreak_uniform_sims_rates$rate_mean, 2)` cases per 1000 patient days \[interquartile (IQR) range `r round(pre_outbreak_uniform_sims_rates$rate_q_low, 2)`--`r round(pre_outbreak_uniform_sims_rates$rate_q_high, 2)`\], compared with the real rate of 1.25 cases per 1000 \[IQR 0.94--1.56\]. During the outbreak period, simulations had a mean rate of `r round(outbreak_uniform_sims_rates$rate_mean, 2)` \[IQR `r round(outbreak_uniform_sims_rates$rate_q_low, 2)`--`r round(outbreak_uniform_sims_rates$rate_q_high, 2)`\] cases, compared with the real mean rate of 3.74 \[IQR 3.32--4.41\] (see @fig-simulated-rates).
